---
output: rmarkdown::github_document
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "inst/extdata/"
)
```
# `gvcR`: Genotypic Variance Components

```{r, echo = FALSE, message = FALSE, warning = FALSE}
devtools::load_all(".")
```

###### Version : [`r getNamespaceVersion("gvcR")`](https://myaseen208.com/gvcR/);  License: [GPL-3](https://www.r-project.org/Licenses/)


##### *Muhammad Yaseen^1,2,3^, Sami Ullah^4^


1. [Asian Development Bank (ADB), Islamabad, Pakistan](https://myaseen208.com/)
2. [Benazir Income Support Programme (BISP), Islamabad, Pakistan](https://myaseen208.com/)
3. [Department of Mathematics and Statistics, University of Agriculture Faisalabad, Pakistan](https://myaseen208.com/)
4. College of Agriculutre, University of Sargodha, Pakistan

***

[![minimal R version](https://img.shields.io/badge/R>%3D-2.10.0-6666ff.svg)](https://cran.r-project.org/)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version-last-release/gvcR)](https://cran.r-project.org/package=gvcR)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/gvcR?color=green)](https://CRAN.R-project.org/package=gvcR)
<!-- [![packageversion](https://img.shields.io/badge/Package%20version-0.2.3.3-orange.svg)](https://github.com/myaseen208/gvcR) -->

```{r, results='asis', echo=FALSE}
dver <- ifelse(test = gsub("(.\\.)(\\d+)(\\..)", "", getNamespaceVersion("gvcR")) != "",
               yes = getNamespaceVersion("gvcR"),
               no = gsub("Version:\\s*", "", readLines(paste0("https://raw.githubusercontent.com/", "myaseen208/gvcR", "/master/DESCRIPTION"))[grep("Version:", readLines(paste0("https://raw.githubusercontent.com/", "myaseen208/gvcR", "/master/DESCRIPTION")))]))
cat(paste("[![develVersion](https://img.shields.io/badge/devel%20version-", dver, "-orange.svg)](https://github.com/myaseen208/gvcR)", sep = ""))
```

<!-- [![GitHub Download Count](https://github-basic-badges.herokuapp.com/downloads/myaseen208/gvcR/total.svg)] -->
[![Project Status: WIP](https://www.repostatus.org/badges/latest/inactive.svg)](https://www.repostatus.org/#inactive)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](https://github.com/myaseen208/gvcR)

***

## Description
`r gsub("(<doi:)(.+)(>)", "[doi:\\2](https://doi.org/\\2)", gsub("\\n", " ", packageDescription("gvcR", fields = "Description")))`

&nbsp;
&nbsp;


## Installation
The package can be installed from CRAN as follows:

```{r, eval=FALSE}
install.packages("gvcR", dependencies = TRUE)
```


&nbsp;


The development version can be installed from github as follows:

```{r, eval=FALSE}
if (!require("remotes")) install.packages("remotes")
remotes::install_github("myaseen208/gvcR")
```

&nbsp;
&nbsp;



## What's new
To know whats new in this version type:

```{r, eval=FALSE}
news(package = "gvcR")
```

## Links

[CRAN page](https://cran.r-project.org/package=gvcR)

[Github page](https://github.com/myaseen208/gvcR)

[Documentation website](https://myaseen208.com/gvcR/)




## Citing `gvcR`
To cite the R package `gvcR` in publications use:


```{r, comment = ""}
citation("gvcR")
```

